Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
work out definitions of AC and SC

\begin{definition}
A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
\end{definition}

@@

\begin{definition}
\label{def:walk}
A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
\end{definition}

@@

\begin{definition}
\label{def:straightBended}
A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
A \defn{corner} is either a peak or a deep (in other words, it is a vertex of~$\omega$ where the arrows change direction).
A walk~$\omega$ is \defn{straight} if it has no corner (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise. Let $\straightWalks(\bar Q)$ and~$\bendingWalks(\bar Q)$ denote the sets of straight and bending walks of~$\bar Q$ and let~$\straightWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \straightWalks(\bar Q)}$ and~$\bendingWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \bendingWalks(\bar Q)}$.
A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep). For~$v \in Q_0$, we denote by~$v_\peak$ the peak walk with peak at~$v$ and by~$v_\deep$ the deep walk with deep~at~$v$.
\end{definition}

@@

\begin{definition}
\label{def:kiss}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$ contains a \emph{finite} substring.
See \fref{fig:kissing}.
% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
%
\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=1]{kissing}}
	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
	\label{fig:kissing}
\end{figure}
%
\end{definition}

\begin{definition}
\label{def:nKc}
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
Note that self-kissing walks never appear in~$\NKC$ by definition.
In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
We thus consider the \defn{reduced non-kissing complex}~$\RNKC$ to be the deletion of all straight walks from~$\NKC$.
\end{definition}

@@

\begin{definition}
\label{def:accordionComplex}
The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex of pairwise non-crossing $\dissection$-accordions.
The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection$-accordions.
\end{definition}

@@

\begin{definition}
\label{def:slalomComplex}
The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex of pairwise non-crossing $\dissection$-slaloms.
The \defn{reduced $\dissection\dual$-slalom complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection\dual$-slaloms.
\end{definition}

>>>>

\begin{definition}
A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
\vincent{Can we delete this notation.}
\end{definition}

@@

\begin{definition}
\label{def:walk}
A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of \defn{undirected walks} of~$\bar Q$.
\vincent{Can we delete this notation.}
\end{definition}

@@

\begin{definition}
\label{def:straightBended}
A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
A \defn{corner} is either a peak or a deep (in other words, it is a vertex of~$\omega$ where the arrows change direction).
A walk~$\omega$ is \defn{straight} if it has no corner (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise.
%Let $\straightWalks(\bar Q)$ and~$\bendingWalks(\bar Q)$ denote the sets of straight and bending walks of~$\bar Q$ and let~$\straightWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \straightWalks(\bar Q)}$ and~$\bendingWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \bendingWalks(\bar Q)}$.
A \defn{peak walk} (resp.~\defn{deep walk}) is a walk with a unique corner (in other words, it switches orientation only once), which is a peak (resp.~deep). For~$v \in Q_0$, we denote by~$v_\peak$ the peak walk with peak at~$v$ and by~$v_\deep$ the deep walk with deep~at~$v$.
\end{definition}

@@

\begin{definition}
\label{def:kiss}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$ contains a \emph{finite} substring.
See \fref{fig:kissing}.
% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
\vincent{Can we delete this notation.}
%
\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=1]{kissing}}
	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
	\label{fig:kissing}
\end{figure}
%
\end{definition}

\begin{definition}
\label{def:nKc}
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
Note that self-kissing walks never appear in~$\NKC$ by definition.
In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-crossing bended walks of~$\bar Q$.
\end{definition}

@@

\begin{definition}
\label{def:accordionComplex}
The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex whose faces are the collections of pairwise non-crossing $\dissection$-accordions.
Note that self-crossing accordions never appear in~$\AC$ by definition.
In contrast, no external accordion can cross another accordion, so that they appear in all facets of~$\AC$. 
The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection$-accordions.
\end{definition}

@@

\begin{definition}
\label{def:slalomComplex}
The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex whose faces are the collections of pairwise non-crossing $\dissection\dual$-slaloms.
Note that self-crossing slalom never appear in~$\SC$ by definition.
In contrast, no external slalom can cross another slalom, so that they appear in all facets of~$\SC$. 
The \defn{reduced $\dissection\dual$-slalom complex}~$\RSC$ is the simplicial complex whose faces are the collections of pairwise non-crossing internal $\dissection\dual$-slaloms.
\end{definition}
